Multi-product Batch Processing Time Maximization Problem

### 2023-07-04 (2023) Fraga et al.tex
updating paper

To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (both available at github.com). The tests were performed on a notebook with an Intel i7 processor. We tested the solvers developed for the benchmarks presented below.

>>>>

To test the developed model and analytical solution method, we created a solver in C++ (https://github.com/tbfraga/project-combinatorial-optimization-problems/tree/main/combinatorial-optimization-solver) and a solver in LINGO (https://github.com/tbfraga/project-combinatorial-optimization-problems/tree/main/lingo-solvers/MPBPTMP). The tests were performed on a notebook with an Intel i7 processor. We tested the solvers developed for the benchmarks presented below (and available on github https://github.com/tbfraga/project-combinatorial-optimization-problems/tree/main/lingo-solvers/MPBPTMP/benchmarcks).
